An algorithm for finding the global extremum\\ of a partially defined function\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-10-03 2023/MMST/samplepaper.tex
replace one reference

A number of efficient deterministic algorithms for solving the Lipschitz global optimization problems have been developed ~\cite{Grishagin2018,Jones2021,PaulaviciusZilinskas2014,Birect2020,Sergeyev2017}. The comparisons conducted have shown the deterministic algorithms outperform (in various criteria) the widespread nature-inspired algorithms ~\cite{Liberti2005,Sergeyev2018}.

>>>>

A number of efficient deterministic algorithms for solving the Lipschitz global optimization problems have been developed ~\cite{Grishagin2016_2,Jones2021,PaulaviciusZilinskas2014,Birect2020,Sergeyev2017}. The comparisons conducted have shown the deterministic algorithms outperform (in various criteria) the widespread nature-inspired algorithms ~\cite{Liberti2005,Sergeyev2018}.
